### 2020-08-04 text/article_vedrovice.Rmd
add spatial analysis: kde, neighbours by buffer

---
title           : "A resampling approach to spatial arrangement and contents of burials in the Vedrovice cemetery"
author          : "Petr Pajdla"
    # name          : "Petr Pajdla"
    # affiliation   : "Department of Archaeology and Museology,
    #                  Masaryk University, Brno, Czech Republic"
    # email         : "petr.pajdla@gmail.com"
date            : "`r format(Sys.time(), '%d %B, %Y')`"
abstract        :
  "Spatial patterns in cemeteries and grave goods associations are often explored using various informal methods.
  We adopt computationaly intensive methods utilizing resampling approaches both to spatial analysis and
  distributions of objects from the Early Neolithic cemetery in Vedrovice.

>>>>

---
title           : "Spatial Analysis and Grave Goods Distribution at the Cemetery of Vedrovice"
# "A resampling approach to spatial arrangement and contents of burials in the Vedrovice cemetery"

author          : "Petr Pajdla"
    # name          : "Petr Pajdla"
    # affiliation   : "Department of Archaeology and Museology,
    #                  Masaryk University, Brno, Czech Republic"
    # email         : "petr.pajdla@gmail.com"
date            : "`r format(Sys.time(), '%d %B, %Y')`"
abstract        :
  "Spatial patterns in cemeteries and grave goods associations are often explored using various informal methods.
  We adopt computationaly intensive methods utilizing resampling approaches both to spatial analysis and
  distributions of objects from the Early Neolithic cemetery in Vedrovice.
